\centerline{\bf ÖZET}
\addcontentsline{toc}{section}{ÖZET}
\begin{center}
\textbf{Projenin Amacý}
\end{center} 
 \mbox{	Web üzerinde responsive olarak çalýþacak mesajlaþma uygulamasý yapmak.}

\begin{center}
\textbf{Projenin Kapsamý}
\end{center}
 \mbox{	Proje kapsamýnda front-end baðlamlarýmý bir arada tutmak için bower compenents kullanarak}
 \mbox{angular dosyalarýmý burada tuttum. Back-end yapýlandýrmalarýmý Node.JS ile gerçekleþtirip veri}
 \mbox{tabanýnda NoSQL yapýsýný tercih edip MongoDB kullandým bunlara ek olarak gerçek zamanlý}
 \mbox{iþlerimi gerçekleþtirebilmek için Ajax yerine Socket.Io ile iþlemlerimi gerçekleþtirdim son olarak}
 \mbox{Redis ile tüm session bilgilerini, mesajlarý, odalarý ve aktif olan kullanýcýlarý tuttum. }
 \mbox{}

\begin{center}
\textbf{Sonuçlar}
\end{center}
 \mbox{	Projenin kapsamýna uyularak ilerlenmiþ ve gerekli tüm yapýlandýrmalar yapýlarak proje digital }
 \mbox{ocean ile canlý ortama taþýnmýþtýr.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%ABSTRACT%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\centerline{\bf ABSTRACT}
\addcontentsline{toc}{section}{ABSTRACT}
\begin{center}
\textbf{Project Objective}
\end{center}

 \mbox{
	Do the messaging app that will run responsibly on the web.}

\begin{center}
\textbf{Scope of Project}
\end{center}
 \mbox{	I kept my angular files using bower compenents to keep my frontend contexts together. I have}
 \mbox{implemented backend configurations with Node.JS and I have chosen the NoSQL structure in}
 \mbox{the database. I used MongoDB to perform real-time tasks in addition to Ajax instead of Socket.Io}
 \mbox{and finally  I used all the session information, messages, chambers and active users with Redis.}

\begin{center}
\textbf{Results}
\end{center}
 \mbox{	The project was carried out in accordance with the scope of the project and all the necessary}
 \mbox{configurations were made and the project was carried to the live environment with the digital}
 \mbox{ ocean.}